---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "Insert title of project here"
subtitle: "Web address for GitHub repository"
author: "Zoe Wong, Molly Bruce"
fontsize: 12pt
mainfont: Times New Roman

---

\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage

```{r setup, include=FALSE}
# Set global options for R chunks
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Set your working directory

# Load your packages
library(tidyverse)
library(ggplot2)
library(reshape2)
library(cowplot)

# Set your ggplot theme
mytheme <- theme_light() +
  theme(axis.text = element_text(color = "black"), 
        legend.position = "top",
        plot.title = element_text(hjust=0.4))
theme_set(mytheme)

# Load your datasets
survey.dat <- read.csv("./Data/Raw/AquacultureSurveyData.csv")

```


# Rationale and Research Questions



## Research Questions

1. (a) When consumers buy seafood, which species do they prefer?  (b) Do they prefer wild or farmed fish?
2. (a) What qualities do consumers associate with wild vs. farmed seafood?  (b) What qualities do they value in seafood?
3. Are seafood values predicted by demographic variables such as age or education level?


\newpage

# Dataset Information

## Description of the Data

Our data were obtained from a social science survey conducted by a multi-university team of researchers, including the Murray lab at Duke University. The survey was conducted in the summer of 2020 via Qualtrics and targeted North Carolina residents from across the state.  

The survey asked respondents a total of 37 questions.  The question topics can be broken down into the following categories: eating habits for 8 types of seafood, what qualities respondents associate with seafood, attitudes about mariculture, attitudes about North Carolina seafood versus commercial fishing, respondents' involvement with seafood production, and demographic indicators. This study focuses on questions about eating habits, what qualities are associated with seafood, and demographic indicators.  

Respondents answered each question by selecting one option from a menu of choices; the number of choices available depended on the question. The dataset contained responses from 1436 participants.

## Data Wrangling

For each analysis, we created a new dataset containing only the relevant columns.  For each category within the survey question, we then created a table with the frequency of each questions response.  For example, one question asked respondents to rate how often they ate each of 8 types of seafood; respondents could choose from 7 responses for each seafood type.  To wrangle this data, we created a dataframe for each type of seafood, for a total of 8 dataframes, each of which contained a column with the response choices and a column with the number of respondents that chose each response.  Because the response choices were only represented by a number in the raw data, we renamed the response column with the meaning of each number for greater clarity.  We repeated this process for the first two research questions (how often participants eat each type of seafood, whether participants prefer each type wild or farmed, whether participants associate each quality with wild or farmed seafood).  

For the third research question, we created a dataframe with responses to a question about how important each of 11 qualities was when respondents were buying seafood.  We then renamed the columns and removed rows with alternate responses to demographic variables, such as "prefer not to answer."

## Data Structure: Consumer preferences

****Data from these responses are categorical, but the response choices could be situated along a linear scale, allowing us to analyze response means. 

Research Question|Survey Question | Response choices
-----------|------------- | --------
1a. When consumers buy seafood, which species do they prefer?   |  In the past year, how often did you eat the following type of seafood**? | 0 = Never, 1 = Once in the past year, 2 = A few times in the past year, 3 = Once a month, 4 = A few times every month, 5 = Once a week, 6 = More than once a week
1b. Do consumers prefer wild or farmed fish? |  Between wild-caught and farmed versions of the same seafood species**, which do you prefer to eat? | 1 = Strongly prefer wild-caught,  2 = Slightly prefer wild-caught,  3 = No preference,  4 = Slightly prefer farmed, 5 = Strongly prefer farmed,  6 = I don't know
2a. What qualities do consumers associate with wild vs. farmed seafood? |  How do you associate the following qualities*** with different types of seafood (farmed and wild-caught)? | 1 = More associated with wild-caught, 2 = Associated equally with wild-caught and farmed, 3 = More associated with farmed,  4 = Associated with neither wild-caught or farmed, 5 = I don't know
2b. What qualities do consumers value in seafood? |  When you are buying seafood, how important are the following qualities*** to you? | 1 = Not at all important, 2 = Slightly important, 3 = Moderately important,   4 = Very important, 5 = Extremely important

 ** Seafood types: Tuna, Shrimp, Salmon, Flounder, Blue Crab, Clams, Mullet, Oysters (8)
 
 *** Qualities: Healthy, Local, Safe, Tasty, Affordable, Sustainable, Fresh, Easy Access, Local Culture, Local Economies, Local Environment (11)

## Data structure: Demographics

Demographic Category | Response choices | Counts
----- | -------- | ---------
Age | 1=19 or younger | 74
.    | 2=20-29 | 201
.    | 3=30-39 | 170
.    | 4=40-49 | 159
.    | 5=50-59 | 156
.    | 6=60-69 | 172
.    | 7=70 or older | 100
.    | 8=Prefer not to answer | 8
Education level | 1=Less than high school | 35
.    | 2=High school graduate | 229
.    | 3=Some college | 302
.    | 4=2 year degree | 167
.    | 5=4 year degree | 382
.    | 6=Professional degree | 260
.    | 7=Doctorate | 49
.    | 8=Prefer not to answer | 12 
Political party | 1=Republican | 449
.    | 2=Democrat | 459
.    | 3=Independent | 384
.    | 4=Other | 28
.    | 5=Prefer not to answer | 116


\newpage

# Exploratory Analysis 

 [explanatory text]
 
```{r freq general}
freq.gen <- as.data.frame(table(survey.dat$Frequency_General))
freq.gen <- freq.gen %>% 
  rename(Response = Var1) %>% 
  mutate(Response = as.numeric(Response) + 1)
freq.gen[7,] <- c(1,0)

freq.response.meaning <- c("2 Once in the past year", 
                           "3 A few times in the past year",
                           "4 Once a month",
                           "5 A few times every month",
                           "6 Once a week",
                           "7 A few times a week",
                           "1 Never")
freq.gen$Response <- freq.response.meaning


freq.general.mean <- freq.general %>% 
  summarize(Overall_Mean = mean(Overall_Frequency))

ggplot(data = freq.gen, aes(x = Response, y = Freq)) +
  geom_bar(stat = "identity") +
  labs(x = "All Seafood", y = "Count", title = "How often did you eat seafood in the last year?") +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.6), 
        plot.title = element_text(hjust=0.5))

```
freq.general mean = 4.76


- map of counties where respondents live?



\newpage

# Analysis



## Question 1a: When consumers buy seafood, which species do they prefer? 

```{r freq violin}
# Selecting the relevant columns from the raw data frame
freq.sp <- select(survey.dat, Frequency_Tuna:Frequency_Oysters)

# Wrangling data for violin plot using pivot_longer
freq.sp.pivot <- freq.sp %>% 
  rename(Tuna = Frequency_Tuna,
         Shrimp = Frequency_Shrimp,
         Salmon = Frequency_Salmon,
         Flounder = Frequency_Flounder,
         BlueCrab = Frequency_BlueCrab,
         Clams = Frequency_Clams,
         Mullet = Frequency_Mullet,
         Oysters = Frequency_Oysters) %>% 
  pivot_longer(Tuna:Oysters, names_to = "Species", values_to = "Response") %>% 
  # Eliminating 0s
  mutate(Response = Response + 1)

freq.pivot.violin <- ggplot() +
  geom_violin(data = freq.sp.pivot, aes(x = Species, y = Response)) +
  geom_point(data = freq.sp.mean, aes(x = Species, y = Mean), size = 3) +
  geom_text(data = freq.sp.mean, aes(x = Species, y = Mean, label = Mean), 
            hjust = -0.5, vjust = -1) +
  labs(title = "How often do you eat certain types of seafood?") + 
  scale_y_continuous(limits = c(1,7), breaks = c(1:7)) +
  theme(plot.title = element_text(hjust=0.5))
freq.pivot.violin

```

[explanation]






```{r frequency, fig.height=8, fig.cap = "How often do you eat the following type of seafood?"}
# Frequency of each response per seafood type
freq.sp.Tuna <- as.data.frame(table(freq.sp$Frequency_Tuna))
freq.sp.Shrimp <- as.data.frame(table(freq.sp$Frequency_Shrimp))
freq.sp.Salmon <- as.data.frame(table(freq.sp$Frequency_Salmon))
freq.sp.Flounder <- as.data.frame(table(freq.sp$Frequency_Flounder))
freq.sp.BlueCrab <- as.data.frame(table(freq.sp$Frequency_BlueCrab))
freq.sp.Clams <- as.data.frame(table(freq.sp$Frequency_Clams))
freq.sp.Mullet <- as.data.frame(table(freq.sp$Frequency_Mullet))
freq.sp.Oysters <- as.data.frame(table(freq.sp$Frequency_Oysters))

# Renaming Response column
freq.response.meaning <- c("1 Never", 
                           "2 Once in the past year", 
                           "3 A few times in the past year",
                           "4 Once a month",
                           "5 A few times every month",
                           "6 Once a week",
                           "7 A few times a week")

freq.sp.Tuna$Var1 <- freq.response.meaning
freq.sp.Shrimp$Var1 <- freq.response.meaning
freq.sp.Salmon$Var1 <- freq.response.meaning
freq.sp.Flounder$Var1 <- freq.response.meaning
freq.sp.BlueCrab$Var1 <- freq.response.meaning
freq.sp.Clams$Var1 <- freq.response.meaning
freq.sp.Mullet$Var1 <- freq.response.meaning
freq.sp.Oysters$Var1 <- freq.response.meaning

# Creating bar plots for each seafood type with consistent axes
freq.Tuna.bar <- ggplot(freq.sp.Tuna, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Tuna") + 
  scale_x_continuous(limits = c(0, 1200), breaks = c(0, 300, 600, 900, 1200))

freq.Shrimp.bar <- ggplot(freq.sp.Shrimp, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Shrimp") + 
  scale_x_continuous(limits = c(0, 1200), breaks = c(0, 300, 600, 900, 1200))

freq.Salmon.bar <- ggplot(freq.sp.Salmon, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Salmon") + 
  scale_x_continuous(limits = c(0, 1200), breaks = c(0, 300, 600, 900, 1200))

freq.Flounder.bar <- ggplot(freq.sp.Flounder, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Flounder") + 
  scale_x_continuous(limits = c(0, 1200), breaks = c(0, 300, 600, 900, 1200))

freq.BlueCrab.bar <- ggplot(freq.sp.BlueCrab, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Blue Crab") + 
  scale_x_continuous(limits = c(0, 1200), breaks = c(0, 300, 600, 900, 1200))

freq.Clams.bar <- ggplot(freq.sp.Clams, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Clams") + 
  scale_x_continuous(limits = c(0, 1200), breaks = c(0, 300, 600, 900, 1200))

freq.Mullet.bar <- ggplot(freq.sp.Mullet, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Mullet") + 
  scale_x_continuous(limits = c(0, 1200), breaks = c(0, 300, 600, 900, 1200))

freq.Oysters.bar <- ggplot(freq.sp.Oysters, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Oysters") + 
  scale_x_continuous(limits = c(0, 1200), breaks = c(0, 300, 600, 900, 1200))

# 4x2 plot presentation
plot_grid(freq.Tuna.bar, freq.Shrimp.bar, freq.Salmon.bar, freq.Flounder.bar, freq.BlueCrab.bar, freq.Clams.bar, freq.Mullet.bar, freq.Oysters.bar, ncol = 2)

```

[explanation of frequency findings]




[explanation etc]








### Question 1b: Do consumers prefer wild or farmed fish?

```{r preference, fig.height=8, fig.cap="Do you prefer wild-caught or farmed versions of these seafood?"}
# Selecting the relevant columns from the raw data frame
pref.sp <- select(survey.dat, Preference_Tuna:Preference_Oysters)

# Frequency of each response per seafood type
pref.sp.Tuna <- as.data.frame(table(pref.sp$Preference_Tuna))
pref.sp.Shrimp <- as.data.frame(table(pref.sp$Preference_Shrimp))
pref.sp.Salmon <- as.data.frame(table(pref.sp$Preference_Salmon))
pref.sp.Flounder <- as.data.frame(table(pref.sp$Preference_Flounder))
pref.sp.BlueCrab <- as.data.frame(table(pref.sp$Preference_BlueCrab))
pref.sp.Clams <- as.data.frame(table(pref.sp$Preference_Clams))
pref.sp.Mullet <- as.data.frame(table(pref.sp$Preference_Mullet))
pref.sp.Oysters <- as.data.frame(table(pref.sp$Preference_Oysters))

# Renaming Response column and removing option 6 "I don't know"
pref.response.meaning <- c("5 Strongly prefer wild caught", 
                           "4 Slightly prefer wild caught", 
                           "3 No preference",
                           "2 Slightly prefer farmed",
                           "1 Strongly prefer farmed")

pref.sp.Tuna <- pref.sp.Tuna[-c(6),]
pref.sp.Tuna$Var1 <- pref.response.meaning
pref.sp.Shrimp <- pref.sp.Shrimp[-c(6),]
pref.sp.Shrimp$Var1 <- pref.response.meaning
pref.sp.Salmon <- pref.sp.Salmon[-c(6),]
pref.sp.Salmon$Var1 <- pref.response.meaning
pref.sp.Flounder <- pref.sp.Flounder[-c(6),]
pref.sp.Flounder$Var1 <- pref.response.meaning
pref.sp.BlueCrab <- pref.sp.BlueCrab[-c(6),]
pref.sp.BlueCrab$Var1 <- pref.response.meaning
pref.sp.Clams <- pref.sp.Clams[-c(6),]
pref.sp.Clams$Var1 <- pref.response.meaning
pref.sp.Mullet <- pref.sp.Mullet[-c(6),]
pref.sp.Mullet$Var1 <- pref.response.meaning
pref.sp.Oysters <- pref.sp.Oysters[-c(6),]
pref.sp.Oysters$Var1 <- pref.response.meaning

# Creating bar plots for each seafood type with consistent axes
pref.Tuna.bar <- ggplot(pref.sp.Tuna, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Tuna") + 
  scale_x_continuous(limits = c(0, 700), breaks = c(0, 200, 400, 600))

pref.Shrimp.bar <- ggplot(pref.sp.Shrimp, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Shrimp") + 
  scale_x_continuous(limits = c(0, 700), breaks = c(0, 200, 400, 600))

pref.Salmon.bar <- ggplot(pref.sp.Salmon, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Salmon") + 
  scale_x_continuous(limits = c(0, 700), breaks = c(0, 200, 400, 600))

pref.Flounder.bar <- ggplot(pref.sp.Flounder, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Flounder") + 
  scale_x_continuous(limits = c(0, 700), breaks = c(0, 200, 400, 600))

pref.BlueCrab.bar <- ggplot(pref.sp.BlueCrab, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Blue Crab") + 
  scale_x_continuous(limits = c(0, 700), breaks = c(0, 200, 400, 600))

pref.Clams.bar <- ggplot(pref.sp.Clams, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Clams") + 
  scale_x_continuous(limits = c(0, 700), breaks = c(0, 200, 400, 600))

pref.Mullet.bar <- ggplot(pref.sp.Mullet, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Mullet") + 
  scale_x_continuous(limits = c(0, 700), breaks = c(0, 200, 400, 600))

pref.Oysters.bar <- ggplot(pref.sp.Oysters, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Oysters") + 
  scale_x_continuous(limits = c(0, 700), breaks = c(0, 200, 400, 600))

# 4x2 plot presentation
plot_grid(pref.Tuna.bar, pref.Shrimp.bar, pref.Salmon.bar, pref.Flounder.bar, pref.BlueCrab.bar, pref.Clams.bar, pref.Mullet.bar, pref.Oysters.bar, ncol = 2)
```

[explanation of findings]







## Question 2a: What qualities do consumers associate with seafood?  

```{r qualities, fig.height = 9, fig.cap="How do you associate the following qualities with wild vs. farmed seafood?"}
# Selecting the relevant columns from the raw data frame
qual.sp <- select(survey.dat, Qualities_Healthy:Qualities_Fresh)

# Frequency of each response per quality
qual.sp.Healthy <- as.data.frame(table(qual.sp$Qualities_Healthy))
qual.sp.Local <- as.data.frame(table(qual.sp$Qualities_Local))
qual.sp.Safe <- as.data.frame(table(qual.sp$Qualities_Safe))
qual.sp.Local_Economies <- as.data.frame(table(qual.sp$Qualities_Local_Economies))
qual.sp.Tasty <- as.data.frame(table(qual.sp$Qualities_Tasty))
qual.sp.Affordable <- as.data.frame(table(qual.sp$Qualities_Affordable))
qual.sp.Local_Culture <- as.data.frame(table(qual.sp$Qualities_Local_Culture))
qual.sp.Sustainable <- as.data.frame(table(qual.sp$Qualities_Sustainable))
qual.sp.Easy_Access <- as.data.frame(table(qual.sp$Qualities_Easy_Access))
qual.sp.Local_Environments <- as.data.frame(table(qual.sp$Qualities_Local_Environments))
qual.sp.Fresh <- as.data.frame(table(qual.sp$Qualities_Fresh))

# Renaming Response column and removing option 5 "I don't know"
qual.response.meaning <- c("4 More associated with wild caught", 
                           "3 Equally associated", 
                           "2 More associated with farmed",
                           "1 Associated w/ neither")

qual.sp.Healthy <- qual.sp.Healthy[-c(5),]
qual.sp.Healthy$Var1 <- qual.response.meaning
qual.sp.Local <- qual.sp.Local[-c(5),]
qual.sp.Local$Var1 <- qual.response.meaning
qual.sp.Safe <- qual.sp.Safe[-c(5),]
qual.sp.Safe$Var1 <- qual.response.meaning
qual.sp.Local_Economies <- qual.sp.Local_Economies[-c(5),]
qual.sp.Local_Economies$Var1 <- qual.response.meaning
qual.sp.Tasty <- qual.sp.Tasty[-c(5),]
qual.sp.Tasty$Var1 <- qual.response.meaning
qual.sp.Affordable <- qual.sp.Affordable[-c(5),]
qual.sp.Affordable$Var1 <- qual.response.meaning
qual.sp.Local_Culture <- qual.sp.Local_Culture[-c(5),]
qual.sp.Local_Culture$Var1 <- qual.response.meaning
qual.sp.Sustainable <- qual.sp.Sustainable[-c(5),]
qual.sp.Sustainable$Var1 <- qual.response.meaning
qual.sp.Easy_Access <- qual.sp.Easy_Access[-c(5),]
qual.sp.Easy_Access$Var1 <- qual.response.meaning
qual.sp.Local_Environments <- qual.sp.Local_Environments[-c(5),]
qual.sp.Local_Environments$Var1 <- qual.response.meaning
qual.sp.Fresh <- qual.sp.Fresh[-c(5),]
qual.sp.Fresh$Var1 <- qual.response.meaning

# Creating bar plots for each quality with consistent axes
qual.Healthy.bar <- ggplot(qual.sp.Healthy, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Healthy") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Local.bar <- ggplot(qual.sp.Local, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Local") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Safe.bar <- ggplot(qual.sp.Safe, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Safe") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Local_Economies.bar <- ggplot(qual.sp.Local_Economies, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Local Economies") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Tasty.bar <- ggplot(qual.sp.Tasty, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Tasty") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Affordable.bar <- ggplot(qual.sp.Affordable, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Affordable") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Local_Culture.bar <- ggplot(qual.sp.Local_Culture, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Local Culture") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Sustainable.bar <- ggplot(qual.sp.Sustainable, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Sustainable") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Easy_Access.bar <- ggplot(qual.sp.Easy_Access, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Easy Access") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Local_Environments.bar <- ggplot(qual.sp.Local_Environments, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Local Environments") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

qual.Fresh.bar <- ggplot(qual.sp.Fresh, aes(y = Var1, x = Freq)) +
  geom_bar(stat = "identity") +
  labs(y = "Response", x = "Count", title = "Fresh") + 
  scale_x_continuous(limits = c(0, 800), breaks = c(0, 400, 800))

# 6x2 plot presentation
plot_grid(qual.Tasty.bar, qual.Fresh.bar, qual.Healthy.bar, qual.Safe.bar, qual.Sustainable.bar, qual.Affordable.bar, qual.Easy_Access.bar, qual.Local.bar, qual.Local_Culture.bar, qual.Local_Economies.bar, qual.Local_Environments.bar, ncol = 2)
```

[explanation of findings]




## Question 2b: What qualities do consumers value in seafood?

```{r importance, fig.cap="How important are the following qualities?"}
importance <- survey.dat %>% 
  select(Importance_Health:Importance_Fresh, Age_corrected, Education, Political_Party) %>% 
   rename(Health = Importance_Health,
         Local = Importance_Local,
         Safe = Importance_Safe,
         Economies = Importance_Local_Economies,
         Tasty = Importance_Tasty,
         Affordable = Importance_Affordable,
         Culture = Importance_Local_Culture,
         Sustainable = Importance_Sustainable,
         Accessibility = Importance_Easy_Access,
         Environment = Importance_Local_Environments,
         Fresh = Importance_Fresh,
         Age = Age_corrected)

columnnames <- c("Age", "Education", "Political_Party")
importance[columnnames] <- lapply(importance[columnnames], factor)

import.summary <- importance %>% 
  summarize(Health = mean(Health),
            Local = mean(Local),
            Safe = mean(Safe),
            Economies = mean(Economies),
            Tasty = mean(Tasty),
            Affordable = mean(Affordable),
            Culture = mean(Culture),
            Sustainable = mean(Sustainable),
            Accessible = mean(Accessibility),
            Environment = mean(Environment),
            Fresh = mean(Fresh)) %>% 
  pivot_longer(Health:Fresh, names_to = "Value", values_to = "Mean")

ggplot(import.summary, aes(x = Value, y = Mean)) +
  geom_point(size = 3) +
  scale_y_continuous(limits = c(1,5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.65), 
        plot.title = element_text(hjust=0.5)) +
  labs(title = "Relative Importance of Values Associated with Seafood", 
       y = "Relative Importance (mean)", 
       x = "Values")
```


## Question 3: Are valued seafood qualities predicted by demographic variables such as age or education level?

Fresh tasty healthy local - qualities most associated with wild

```{r}
# Creating separate dataframes per variable to eliminate unwanted rows
demo.age <- importance %>% 
  filter(Age != 8)

demo.ed <- importance %>% 
  filter(Education != 8)

demo.party <- importance %>% 
  filter(Political_Party == 1 | Political_Party == 2)
```


```{r fresh demo}
fresh.lm.age <- lm(data = demo.age, Fresh ~ Age)
summary(fresh.lm.age) 

fresh.lm.education <- lm(data = demo.ed, Fresh ~ Education)
summary(fresh.lm.education)

fresh.lm.political <- lm(data = demo.party, Fresh ~ Political_Party)
summary(fresh.lm.political)
```

```{r local}
local.lm.age <- lm(data = demo.age, Local ~ Age)
summary(local.lm.age) #age 6 cares slightly more

local.lm.education <- lm(data = demo.ed, Local ~ Education)
summary(local.lm.education) # ed3 significant

local.lm.political <- lm(data = demo.party, Local ~ Political_Party)
summary(local.lm.political) # no significance
```

```{r tasty}
tasty.lm.age <- lm(data = demo.age, Tasty ~ Age)
summary(tasty.lm.age) #age 6 cares slightly more

tasty.lm.education <- lm(data = demo.ed, Tasty ~ Education)
summary(tasty.lm.education) # ed3 significant

tasty.lm.political <- lm(data = demo.party, Tasty ~ Political_Party)
summary(tasty.lm.political) # no significance
```

```{r healthy}
health.lm.age <- lm(data = demo.age, Health ~ Age)
summary(health.lm.age) #age 6 cares slightly more

health.lm.education <- lm(data = demo.ed, Health ~ Education)
summary(health.lm.education) # ed3 significant

health.lm.political <- lm(data = demo.party, Health ~ Political_Party)
summary(health.lm.political) # no significance
```


\newpage

# Summary and Conclusions


\newpage

# References
<add references here if relevant, otherwise delete this section> 