---
title: "Working_File"
author: "Zoe Wong"
date: "4/9/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

```{r setup}
getwd()
library(tidyverse)

survey.dat <- read.csv("./AquacultureSurveyData.csv")
survey.codes <- read.csv("./AquacultureSurveyCodes.csv")

# Set ggplot theme
mytheme <- theme_classic() +
  theme(axis.text = element_text(color = "black"), 
        legend.position = "top")
theme_set(mytheme)
```


## Basic overview questions

1. Make a dataframe just for species-related data - general analysis
      -> work w/ separate dataframes for each type of data (frequency, form, etc)?
      -> only use Tuna:Oysters since no category but frequency asks about raw forms
      -> omit Frequency_General - can analyze separately if necessary
2. Find frequency of each response
3. General overview questions:  
      *What are the most common species consumed?
      *Where do people get their seafood?  
      *How do people prefer to buy their seafood?
      *Do people prefer wild-caught or farmed seafood?

```{r frequency} 
freq.sp <- select(survey.dat, Frequency_Tuna:Frequency_Oysters)

freq.sp.Tuna <- as.data.frame(table(freq.sp$Frequency_Tuna))
freq.sp.Shrimp <- as.data.frame(table(freq.sp$Frequency_Shrimp))
freq.sp.Salmon <- as.data.frame(table(freq.sp$Frequency_Salmon))
freq.sp.Flounder <- as.data.frame(table(freq.sp$Frequency_Flounder))
freq.sp.BlueCrab <- as.data.frame(table(freq.sp$Frequency_BlueCrab))
freq.sp.Clams <- as.data.frame(table(freq.sp$Frequency_Clams))
freq.sp.Mullet <- as.data.frame(table(freq.sp$Frequency_Mullet))
freq.sp.Oysters <- as.data.frame(table(freq.sp$Frequency_Oysters))

freq.sp.summary <- freq.sp.Tuna %>% 
  left_join(freq.sp.Shrimp, by = "Var1") %>% 
  left_join(freq.sp.Salmon, by = "Var1") %>% 
  left_join(freq.sp.Flounder, by = "Var1") %>% 
  left_join(freq.sp.BlueCrab, by = "Var1") %>% 
  left_join(freq.sp.Clams, by = "Var1") %>% 
  left_join(freq.sp.Mullet, by = "Var1") %>% 
  left_join(freq.sp.Oysters, by = "Var1")
freq.sp.summary <- freq.sp.summary %>% 
  rename(Response = Var1,
         Tuna = Freq.x,
         Shrimp = Freq.y,
         Salmon = Freq.x.x,
         Flounder = Freq.y.y,
         BlueCrab = Freq.x.x.x,
         Clams = Freq.y.y.y,
         Mullet = Freq.x.x.x.x,
         Oysters = Freq.y.y.y.y)
```

## Notes on responses 

0. Never 
1. Once in the past year 
2. A few times in the past year 
3. Once a month 
4. A few times every month 
5. Once a week 
6. A few times a week 

```{r How Often Plot}
ggplot(freq.sp.summary,aes(x=Response, y=Tuna)) + 
  geom_point() + 
  labs(title ="In the past year, how often did you eat Tuna?",
       y="Count of Response Type",
       x="Response") + 
  theme(plot.title = element_text(hjust=0.5))
```

```{r where}
where.sp <- select(survey.dat, Where_Tuna:Where_Oysters)

where.sp.Tuna <- as.data.frame(table(where.sp$Where_Tuna))
where.sp.Shrimp <- as.data.frame(table(where.sp$Where_Shrimp))
where.sp.Salmon <- as.data.frame(table(where.sp$Where_Salmon))
where.sp.Flounder <- as.data.frame(table(where.sp$Where_Flounder))
where.sp.BlueCrab <- as.data.frame(table(where.sp$Where_BlueCrab))
where.sp.Clams <- as.data.frame(table(where.sp$Where_Clams))
where.sp.Mullet <- as.data.frame(table(where.sp$Where_Mullet))
where.sp.Oysters <- as.data.frame(table(where.sp$Where_Oysters))

where.sp.summary <- where.sp.Tuna %>% 
  left_join(where.sp.Shrimp, by = "Var1") %>% 
  left_join(where.sp.Salmon, by = "Var1") %>% 
  left_join(where.sp.Flounder, by = "Var1") %>% 
  left_join(where.sp.BlueCrab, by = "Var1") %>% 
  left_join(where.sp.Clams, by = "Var1") %>% 
  left_join(where.sp.Mullet, by = "Var1") %>% 
  left_join(where.sp.Oysters, by = "Var1")
where.sp.summary <- where.sp.summary %>% 
  rename(Response = Var1,
         Tuna = Freq.x,
         Shrimp = Freq.y,
         Salmon = Freq.x.x,
         Flounder = Freq.y.y,
         BlueCrab = Freq.x.x.x,
         Clams = Freq.y.y.y,
         Mullet = Freq.x.x.x.x,
         Oysters = Freq.y.y.y.y)
```

## Notes on responses 

1. Caught or grown myself 
2. Caught or grown by a friend or family member 
3. Grocery store 
4. Restaurant 
5. Seafood market 
6. Commercial fisherman or seafood farmer 
7. Community-supported fishery (CSF)
8. Other

```{r Where Plot}
ggplot(where.sp.summary,aes(x=Response, y=Tuna)) + 
  geom_point() + 
  labs(title ="Tuna: Where do you get your seafood?",
       y="Count of Response Type",
       x="Response") + 
  theme(plot.title = element_text(hjust=0.5))
```


## Attitude analysis

```{r}

```

