---
title: "Working_File"
author: "Zoe Wong"
date: "4/9/2021"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup

```{r setup}
getwd()
library(tidyverse)
library(ggplot2)
library(reshape2)

survey.dat <- read.csv("./AquacultureSurveyData.csv")
survey.codes <- read.csv("./AquacultureSurveyCodes.csv")

# Set ggplot theme
mytheme <- theme_light() +
  theme(axis.text = element_text(color = "black"), 
        legend.position = "top")
theme_set(mytheme)
```

# Basic overview questions

1. Make a dataframe just for species-related data - general analysis
      -> work w/ separate dataframes for each type of data (frequency, form, etc)?
      -> only use Tuna:Oysters since no category but frequency asks about raw forms
      -> omit Frequency_General - can analyze separately if necessary
2. Find frequency of each response
3. General overview questions:  
      *What are the most common species consumed?
      *Where do people get their seafood?  
      *How do people prefer to buy their seafood?
      *Do people prefer wild-caught or farmed seafood?

## Frequency Analysis

```{r frequency} 
freq.sp <- select(survey.dat, Frequency_Tuna:Frequency_Oysters)

freq.sp.Tuna <- as.data.frame(table(freq.sp$Frequency_Tuna))
freq.sp.Shrimp <- as.data.frame(table(freq.sp$Frequency_Shrimp))
freq.sp.Salmon <- as.data.frame(table(freq.sp$Frequency_Salmon))
freq.sp.Flounder <- as.data.frame(table(freq.sp$Frequency_Flounder))
freq.sp.BlueCrab <- as.data.frame(table(freq.sp$Frequency_BlueCrab))
freq.sp.Clams <- as.data.frame(table(freq.sp$Frequency_Clams))
freq.sp.Mullet <- as.data.frame(table(freq.sp$Frequency_Mullet))
freq.sp.Oysters <- as.data.frame(table(freq.sp$Frequency_Oysters))

freq.sp.summary <- freq.sp.Tuna %>% 
  left_join(freq.sp.Shrimp, by = "Var1") %>% 
  left_join(freq.sp.Salmon, by = "Var1") %>% 
  left_join(freq.sp.Flounder, by = "Var1") %>% 
  left_join(freq.sp.BlueCrab, by = "Var1") %>% 
  left_join(freq.sp.Clams, by = "Var1") %>% 
  left_join(freq.sp.Mullet, by = "Var1") %>% 
  left_join(freq.sp.Oysters, by = "Var1")
freq.sp.summary <- freq.sp.summary %>% 
  rename(Response = Var1,
         Tuna = Freq.x,
         Shrimp = Freq.y,
         Salmon = Freq.x.x,
         Flounder = Freq.y.y,
         BlueCrab = Freq.x.x.x,
         Clams = Freq.y.y.y,
         Mullet = Freq.x.x.x.x,
         Oysters = Freq.y.y.y.y)

freq.response.meaning <- c("1 Never", 
                           "2 Once in the past year", 
                           "3 A few times in the past year",
                           "4 Once a month",
                           "5 A few times every month",
                           "6 Once a week",
                           "7 A few times a week")

freq.sp.summary$Response_Explanation <- freq.response.meaning

#melt data frame into long format
freq.sp.summary.long <- melt(freq.sp.summary,  id.vars = 'Response_Explanation', variable.name = 'series')
freq.sp.summary.long <- freq.sp.summary.long[-c(1, 2, 3, 4, 5, 6, 7), ]
freq.sp.summary.long$value <- as.numeric(freq.sp.summary.long$value)

#create plot for each column in data frame
ggplot(freq.sp.summary.long, aes(y=Response_Explanation, x=value)) +
  geom_point(aes(colour = series)) + 
  labs(title ="How often do you eat different seafood types?",
       x="Number of responses",
       y="Response",
       color = "Type") + 
  theme(axis.text.x = element_text(angle = 45), 
        plot.title = element_text(hjust=0.5))

```

### Frequency visualization 1

```{r}
#which species are eaten most frequently
freq.sp.summary$Response <- as.numeric(freq.sp.summary$Response)
freq.sp.summary.which <- freq.sp.summary %>% 
  mutate(Tuna.freq = Tuna * Response,
         Shrimp.freq = Shrimp * Response,
         Salmon.freq = Salmon * Response,
         Flounder.freq = Flounder * Response,
         BlueCrab.freq = BlueCrab * Response,
         Clams.freq = Clams * Response,
         Mullet.freq = Mullet * Response,
         Oysters.freq = Oysters * Response) %>% 
  select(Response, Response_Explanation:Oysters.freq) %>% 
  summarize(Tuna = mean(Tuna.freq),
            Shrimp = mean(Shrimp.freq),
            Salmon = mean(Salmon.freq),
            Flounder = mean(Flounder.freq),
            BlueCrab = mean(BlueCrab.freq),
            Clams = mean(Clams.freq),
            Mullet = mean(Mullet.freq),
            Oysters = mean(Oysters.freq)) %>% 
  pivot_longer(Tuna:Oysters, names_to = "Species", values_to = "ResponseMean")

#plot most frequently eaten sp
ggplot(freq.sp.summary.which) +
  geom_point(aes(y = Species, x = ResponseMean)) + 
  labs(title = "Title", 
       y = "Number of Responses", 
       x = "Species") + 
  theme(axis.text.x = element_text(angle = 45), 
        plot.title = element_text(hjust=0.5))
```

### Frequency visualization 2 (better)

```{r}
freq.sp.pivot <- freq.sp %>% 
  rename(Tuna = Frequency_Tuna,
         Shrimp = Frequency_Shrimp,
         Salmon = Frequency_Salmon,
         Flounder = Frequency_Flounder,
         BlueCrab = Frequency_BlueCrab,
         Clams = Frequency_Clams,
         Mullet = Frequency_Mullet,
         Oysters = Frequency_Oysters) %>% 
  pivot_longer(Tuna:Oysters, names_to = "Species", values_to = "Response") %>% 
  mutate(Response = Response + 1)

freq.sp.mean <- freq.sp %>% 
  mutate(Frequency_Tuna = Frequency_Tuna + 1,
         Frequency_Shrimp = Frequency_Shrimp + 1,
         Frequency_Salmon = Frequency_Salmon + 1,
         Frequency_Flounder = Frequency_Flounder + 1,
         Frequency_BlueCrab = Frequency_BlueCrab + 1,
         Frequency_Clams = Frequency_Clams + 1,
         Frequency_Mullet = Frequency_Mullet + 1,
         Frequency_Oysters = Frequency_Oysters + 1) %>% 
  summarize(Tuna = mean(Frequency_Tuna),
            Shrimp = mean(Frequency_Shrimp),
            Salmon = mean(Frequency_Salmon),
            Flounder = mean(Frequency_Flounder),
            BlueCrab = mean(Frequency_BlueCrab),
            Clams = mean(Frequency_Clams),
            Mullet = mean(Frequency_Mullet),
            Oysters = mean(Frequency_Oysters)) %>% 
  pivot_longer(Tuna:Oysters, names_to = "Species", values_to = "Mean")

# Violin plot
freq.pivot.violin <- ggplot() +
  geom_violin(data = freq.sp.pivot, aes(x = Species, y = Response)) +
  geom_point(data = freq.sp.mean, aes(x = Species, y = Mean), size = 3) +
  labs(title = "How often do you eat certain seafood?") + 
  scale_y_continuous(limits = c(1,7), breaks = c(1:7)) +
  theme(plot.title = element_text(hjust=0.5))
freq.pivot.violin

# Box plot
freq.pivot.box <-
  ggplot(freq.sp.pivot, aes(y = Species, x = Response)) +
  geom_boxplot()
freq.pivot.box
```

## Where/Source Analysis

```{r where}
where.sp <- select(survey.dat, Where_Tuna:Where_Oysters)

where.sp.Tuna <- as.data.frame(table(where.sp$Where_Tuna))
where.sp.Shrimp <- as.data.frame(table(where.sp$Where_Shrimp))
where.sp.Salmon <- as.data.frame(table(where.sp$Where_Salmon))
where.sp.Flounder <- as.data.frame(table(where.sp$Where_Flounder))
where.sp.BlueCrab <- as.data.frame(table(where.sp$Where_BlueCrab))
where.sp.Clams <- as.data.frame(table(where.sp$Where_Clams))
where.sp.Mullet <- as.data.frame(table(where.sp$Where_Mullet))
where.sp.Oysters <- as.data.frame(table(where.sp$Where_Oysters))

where.sp.summary <- where.sp.Tuna %>% 
  left_join(where.sp.Shrimp, by = "Var1") %>% 
  left_join(where.sp.Salmon, by = "Var1") %>% 
  left_join(where.sp.Flounder, by = "Var1") %>% 
  left_join(where.sp.BlueCrab, by = "Var1") %>% 
  left_join(where.sp.Clams, by = "Var1") %>% 
  left_join(where.sp.Mullet, by = "Var1") %>% 
  left_join(where.sp.Oysters, by = "Var1")
where.sp.summary <- where.sp.summary %>% 
  rename(Response = Var1,
         Tuna = Freq.x,
         Shrimp = Freq.y,
         Salmon = Freq.x.x,
         Flounder = Freq.y.y,
         BlueCrab = Freq.x.x.x,
         Clams = Freq.y.y.y,
         Mullet = Freq.x.x.x.x,
         Oysters = Freq.y.y.y.y)

where.response.meaning <- c("Caught or grown myself", 
                           "Caught or grown by a friend or family member", 
                           "Grocery store",
                           "Restaurant",
                           "Seafood market",
                           "Commercial fisherman or seafood farmer",
                           "Community-supported fishery (CSF)",
                           "Other")

where.sp.summary$Response_Explanation <- where.response.meaning

#melt data frame into long format
where.sp.summary.long <- melt(where.sp.summary,  id.vars = 'Response_Explanation', variable.name = 'series')
where.sp.summary.long <- where.sp.summary.long[-c(1, 2, 3, 4, 5, 6, 7, 8), ]
where.sp.summary.long$value <- as.numeric(where.sp.summary.long$value)

#create plot for each column in data frame
ggplot(where.sp.summary.long, aes(y=Response_Explanation, x=value)) +
  geom_point(aes(colour = series)) + 
  labs(title ="Where do you get your seafood?",
       x="Count of Response Type",
       y="Response") + 
  theme(axis.text.x = element_text(angle = 90), 
        plot.title = element_text(hjust=0.5))
```

## Preference analysis

```{r preference}
pref.sp <- select(survey.dat, Preference_Tuna:Preference_Oysters)

pref.sp.Tuna <- as.data.frame(table(pref.sp$Preference_Tuna))
pref.sp.Shrimp <- as.data.frame(table(pref.sp$Preference_Shrimp))
pref.sp.Salmon <- as.data.frame(table(pref.sp$Preference_Salmon))
pref.sp.Flounder <- as.data.frame(table(pref.sp$Preference_Flounder))
pref.sp.BlueCrab <- as.data.frame(table(pref.sp$Preference_BlueCrab))
pref.sp.Clams <- as.data.frame(table(pref.sp$Preference_Clams))
pref.sp.Mullet <- as.data.frame(table(pref.sp$Preference_Mullet))
pref.sp.Oysters <- as.data.frame(table(pref.sp$Preference_Oysters))

pref.sp.summary <- pref.sp.Tuna %>% 
  left_join(pref.sp.Shrimp, by = "Var1") %>% 
  left_join(pref.sp.Salmon, by = "Var1") %>% 
  left_join(pref.sp.Flounder, by = "Var1") %>% 
  left_join(pref.sp.BlueCrab, by = "Var1") %>% 
  left_join(pref.sp.Clams, by = "Var1") %>% 
  left_join(pref.sp.Mullet, by = "Var1") %>% 
  left_join(pref.sp.Oysters, by = "Var1")
pref.sp.summary <- pref.sp.summary %>% 
  rename(Response = Var1,
         Tuna = Freq.x,
         Shrimp = Freq.y,
         Salmon = Freq.x.x,
         Flounder = Freq.y.y,
         BlueCrab = Freq.x.x.x,
         Clams = Freq.y.y.y,
         Mullet = Freq.x.x.x.x,
         Oysters = Freq.y.y.y.y)

pref.sp.summary <- pref.sp.summary[-c(6),]

pref.response.meaning <- c("5 Strongly prefer wild caught", 
                           "4 Slightly prefer wild caught", 
                           "3 No preference",
                           "2 Slightly prefer farmed",
                           "1 Strongly prefer farmed")

pref.sp.summary$Response_Explanation <- pref.response.meaning

#melt data frame into long format
pref.sp.summary.long <- melt(pref.sp.summary,  id.vars = 'Response_Explanation', variable.name = 'series')
pref.sp.summary.long <- pref.sp.summary.long[-c(1, 2, 3, 4, 5, 6), ]
pref.sp.summary.long$value <- as.numeric(pref.sp.summary.long$value)

#create plot for each column in data frame
ggplot(pref.sp.summary.long, aes(y=Response_Explanation, x=value)) +
  geom_point(aes(colour = series), size = 3) + 
  labs(title ="Wild caught vs farmed preferences for different seafood types",
       x="Count of Response Type",
       y="Response") + 
  theme(axis.text.x = element_text(angle = 45), 
        plot.title = element_text(hjust=0.5))
```

## Qualities analysis 

```{r qualities}
qual.sp <- select(survey.dat, Qualities_Healthy:Qualities_Fresh)

qual.sp.Healthy <- as.data.frame(table(qual.sp$Qualities_Healthy))
qual.sp.Local <- as.data.frame(table(qual.sp$Qualities_Local))
qual.sp.Safe <- as.data.frame(table(qual.sp$Qualities_Safe))
qual.sp.Local_Economies <- as.data.frame(table(qual.sp$Qualities_Local_Economies))
qual.sp.Tasty <- as.data.frame(table(qual.sp$Qualities_Tasty))
qual.sp.Affordable <- as.data.frame(table(qual.sp$Qualities_Affordable))
qual.sp.Local_Culture <- as.data.frame(table(qual.sp$Qualities_Local_Culture))
qual.sp.Sustainable <- as.data.frame(table(qual.sp$Qualities_Sustainable))
qual.sp.Easy_Access <- as.data.frame(table(qual.sp$Qualities_Easy_Access))
qual.sp.Local_Environments <- as.data.frame(table(qual.sp$Qualities_Local_Environments))
qual.sp.Fresh <- as.data.frame(table(qual.sp$Qualities_Fresh))

qual.sp.summary <- qual.sp.Healthy %>% 
  left_join(qual.sp.Local, by = "Var1") %>% 
  left_join(qual.sp.Safe, by = "Var1") %>% 
  left_join(qual.sp.Local_Economies, by = "Var1") %>% 
  left_join(qual.sp.Tasty, by = "Var1") %>% 
  left_join(qual.sp.Affordable, by = "Var1") %>% 
  left_join(qual.sp.Local_Culture, by = "Var1") %>% 
  left_join(qual.sp.Sustainable, by = "Var1") %>%
  left_join(qual.sp.Easy_Access, by = "Var1") %>%
  left_join(qual.sp.Local_Environments, by = "Var1") %>%
  left_join(qual.sp.Fresh, by = "Var1")
qual.sp.summary <- qual.sp.summary %>% 
  rename(Response = Var1,
         Healthy = Freq.x,
         Local = Freq.y,
         Safe = Freq.x.x,
         LocalEconomies = Freq.y.y,
         Tasty = Freq.x.x.x,
         Affordable = Freq.y.y.y,
         LocalCulture = Freq.x.x.x.x,
         Sustainable = Freq.y.y.y.y,
         EasyAccess = Freq.x.x.x.x.x,
         LocalEnvironments = Freq.y.y.y.y.y,
         Fresh = Freq)

qual.sp.summary <- qual.sp.summary[-c(5),]

qual.response.meaning <- c("4 More associated with wild caught", 
                           "3 Equally associated w/ wild caught & farmed", 
                           "2 More associated with farmed",
                           "1 Associated w/ neither wild caught nor farmed")

qual.sp.summary$Response_Explanation <- qual.response.meaning

#melt data frame into long format
qual.sp.summary.long <- melt(qual.sp.summary,  id.vars = 'Response_Explanation', variable.name = 'series')
qual.sp.summary.long <- qual.sp.summary.long[-c(1, 2, 3, 4, 5), ]
qual.sp.summary.long$value <- as.numeric(qual.sp.summary.long$value)

#create plot for each column in data frame
ggplot(qual.sp.summary.long, aes(y=Response_Explanation, x=value)) +
  geom_point(aes(colour = series), size = 3) + 
  labs(title ="Quality associations with wild vs farmed seafood",
       x="Count",
       y="Response") + 
  theme(axis.text.x = element_text(angle = 90), 
        plot.title = element_text(hjust=0.5))
```

## Importance analysis

```{r importance}
importance <- survey.dat %>% 
  select(Importance_Health:Importance_Farmed, Age_corrected, Gender_original, Education, Political_Party, Race1, Income) %>% 
   rename(Health = Importance_Health,
         Local = Importance_Local,
         Safe = Importance_Safe,
         Economies = Importance_Local_Economies,
         Tasty = Importance_Tasty,
         Affordable = Importance_Affordable,
         Culture = Importance_Local_Culture,
         Sustainable = Importance_Sustainable,
         Accessibility = Importance_Easy_Access,
         Environment = Importance_Local_Environments,
         Fresh = Importance_Fresh,
         Wild = Importance_Wild,
         Farmed = Importance_Farmed,
         Age = Age_corrected,
         Gender = Gender_original) %>% 
  filter(Education != 8, Gender == 1 | Gender == 2, Age != 8, Political_Party == 1 | Political_Party == 2, Race1 != 8 | Race1 != 9, Income != 8)

columnnames <- c("Age", "Gender", "Education", "Political_Party", "Race1", "Income")
importance[columnnames] <- lapply(importance[columnnames], factor)

import.pivot <- importance %>% 
  pivot_longer(Health:Farmed, names_to = "Value", values_to = "Response")

# Box plot
import.pivot.box <-
  ggplot(import.pivot, aes(x = Value, y = Response)) +
  geom_boxplot()
import.pivot.box  #doesn't show much honestly

# exploring demographics to see if there are any w/ few numbers
summary(importance$Age)
summary(importance$Gender)
summary(importance$Education) #only 7 people at ed level 7 doctorate
summary(importance$Political_Party)
summary(importance$Race1) #low numbers of 4-7 - might want to narrow to just 1, 2, 3 (white, latino, black)
summary(importance$Income)

# distribution of selected values
sust <- summary(importance$Sustainable)
sust[4]

import.summary <- importance %>% 
  summarize(Health = mean(Health),
            Local = mean(Local),
            Safe = mean(Safe),
            Economies = mean(Economies),
            Tasty = mean(Tasty),
            Affordable = mean(Affordable),
            Culture = mean(Culture),
            Sustainable = mean(Sustainable),
            Accessible = mean(Accessibility),
            Environment = mean(Environment),
            Fresh = mean(Fresh),
            Wild = mean(Wild),
            Farmed = mean(Farmed)) %>% 
  pivot_longer(Health:Farmed, names_to = "Value", values_to = "Mean")

ggplot(import.summary, aes(x = Value, y = Mean)) +
  geom_point(size = 3) +
  scale_y_continuous(limits = c(1,5)) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.65), 
        plot.title = element_text(hjust=0.5)) +
  labs(title = "Relative Importance of Values Associated with Seafood", 
       y = "Relative Importance (mean)", 
       x = "Values")
```

```{r wild}
#models
importance.lm.age <- lm(data = importance, Wild ~ Age)
summary(importance.lm.age) #older people care more about wild?

importance.lm.gender <- lm(data = importance, Wild ~ Gender)
summary(importance.lm.gender) # no difference

importance.lm.education <- lm(data = importance, Wild ~ Education)
summary(importance.lm.education) # ed3 significant

importance.lm.political <- lm(data = importance, Wild ~ Political_Party)
summary(importance.lm.political) # no significance

importance.lm.race <- lm(data = importance, Wild ~ Race1)
summary(importance.lm.race) # no significance

importance.lm.income <- lm(data = importance, Wild ~ Income)
summary(importance.lm.income) # 

importance.lm.age.gender <- lm(data = importance, Wild ~ Age * Gender)
summary(importance.lm.age.gender) #

importance.plot <- ggplot(importance, aes(x = Education, y = Wild)) +
  geom_jitter()
importance.plot
```

```{r fresh}
#models
fresh.lm.age <- lm(data = importance, Fresh ~ Age)
summary(fresh.lm.age) #older people care more about fresh

fresh.lm.gender <- lm(data = importance, Fresh ~ Gender)
summary(fresh.lm.gender) # no difference

fresh.lm.education <- lm(data = importance, Fresh ~ Education)
summary(fresh.lm.education) # ed3 significant

fresh.lm.political <- lm(data = importance, Fresh ~ Political_Party)
summary(fresh.lm.political) # no significance

fresh.lm.race <- lm(data = importance, Fresh ~ Race1)
summary(fresh.lm.race) # no significance

fresh.lm.income <- lm(data = importance, Fresh ~ Income)
summary(fresh.lm.income) # no significance

fresh.lm.age.gender <- lm(data = importance, Fresh ~ Age * Gender)
summary(fresh.lm.age.gender) #

#example plot?
fresh.plot <- ggplot(importance, aes(x = Education, y = Fresh)) +
  geom_jitter()
fresh.plot
```

```{r Sustainable}
summary(importance$Sustainable)

sust.lm.age <- lm(data = importance, Sustainable ~ Age)
summary(sust.lm.age) #age 6 cares slightly more

sust.lm.gender <- lm(data = importance, Sustainable ~ Gender)
summary(sust.lm.gender) # no difference

sust.lm.education <- lm(data = importance, Sustainable ~ Education)
summary(sust.lm.education) # ed3 significant

sust.lm.political <- lm(data = importance, Sustainable ~ Political_Party)
summary(sust.lm.political) # no significance

sust.lm.race <- lm(data = importance, Sustainable ~ Race1)
summary(sust.lm.race) # no significance

sust.lm.income <- lm(data = importance, Sustainable ~ Income)
summary(sust.lm.income) # no significance

sust.lm.age.gender <- lm(data = importance, Sustainable ~ Age * Gender)
summary(sust.lm.age.gender) #

sust.plot <- ggplot(importance, aes(x = Education, y = Sustainable)) +
  geom_jitter()
sust.plot
```

```{r local}
summary(importance$Local)

local.lm.age <- lm(data = importance, Local ~ Age)
summary(local.lm.age) #age 6 cares slightly more

local.lm.gender <- lm(data = importance, Local ~ Gender)
summary(local.lm.gender) # no difference

local.lm.education <- lm(data = importance, Local ~ Education)
summary(local.lm.education) # ed3 significant

local.lm.political <- lm(data = importance, Local ~ Political_Party)
summary(local.lm.political) # no significance

local.lm.race <- lm(data = importance, Local ~ Race1)
summary(local.lm.race) # no significance

local.lm.income <- lm(data = importance, Local ~ Income)
summary(local.lm.income) # no significance

local.lm.age.gender <- lm(data = importance, Local ~ Age * Gender)
summary(local.lm.age.gender) #

local.plot <- ggplot(importance, aes(x = Education, y = Local)) +
  geom_jitter()
local.plot
```

